\documentclass[]{cv_class}

\begin{document}

\lastupdated
%\photo{me.jpg}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Theo}{Windebank}{ \urlstyle{same}\url{theowindebank.co.uk} \\
\href{mailto:theo.windebank@stcatz.ox.ac.uk}{theo.windebank@stcatz.ox.ac.uk} | 07849199189}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{3\topsep}
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{University of Oxford}
\descript{MEng | Engineering Science}
\location{St. Catherine's College (2013 - 2017)}
{\fontspec{Helvetica Neue Light}Current Modules:}
\begin{minitemize}
\item Engineering Computation
\item Information Engineering Systems
\item Control Systems
\item Software Engineering
\item Biomechanics
\item Biomedical Modelling and Monitoring
\end{minitemize}
{\fontspec{Helvetica Neue Thin} Predicted:} 2.i
\sectionsep

\subsection{\normalsize Queen Elizabeth High School}
\location{Hexham (2008 - 2013)}
\vspace{-\topsep}
\begin{minitemize}
\item A* {\fontspec{Helvetica Neue Thin} Maths}
\item A* {\fontspec{Helvetica Neue Thin} Further Maths}
\item A* {\fontspec{Helvetica Neue Thin} Physics}
\item A 	{\fontspec{Helvetica Neue Thin} Product Design}
\item A 	{\fontspec{Helvetica Neue Thin} Extended Project}
\end{minitemize}
\vspace{-\topsep}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%LinkedIn://  \href{https://www.linkedin.com/in/theowindebank}{\custombold{theowindebank}} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
\subsection{Coursework}
Saving Oneself \textit{\fontspec{Helvetica Neue Thin}current}\\
\projectinf{Looking at imaging and processing the human brain to map the 'connectome'.}
Android Development\\
\projectinf{Coded a calculator in Java.}
Mobile Robots\\
\projectinf{Programmed microcontrollers in C to make a robot dynamically follow a course.}
Mechanical CAD
\sectionsep

\subsection{Personal}
Raspberry Pi Cocktail Dispenser \textit{\fontspec{Helvetica Neue Thin}current}\\
\projectinf{Built and programmed a web interface to remotely dispense cocktails.}
\sectionsep

\subsection{Other}
Engineers Without Borders \textit{\fontspec{Helvetica Neue Thin}current}\\
\projectinf{Working on a database system to collect and process information on malaria cases in rural Peru.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\experience{Newcastle University}{http://www.ncl.ac.uk/eee/research/groups/coms2ip/}
\descript{| Research Assistant for Communications, Sensors, Signal \& Information Processing Group}
\location{July 2015 – Sep 2015 | Newcastle upon Tyne, UK}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on various sonar systems to image undersea objects beneath sand.
\item Explored a variety of techniques such as delay-sum beamforming, synthetic aperture focusing and signal filtering.
\end{tightemize}
\sectionsep

\experience{Skalene}{http://www.skalene.com/}
\descript{| Modelling \& Analysis Technician }
\location{July 2014 – April 2015 | Cambridge, UK}
\begin{tightemize}
\item Worked on a cheap and compact PCR (Polymerase Chain Reaction) unit used to amplify DNA. 
\item Simulated and analysed heat flow between parts of the PCR in order to maintain a uniform heat distribution. 
\item Improved data analysis skill set.
\item Gained experience with FEM modules of SolidWorks.
\end{tightemize}
\sectionsep

\experience{Royal Air Force}{http://www.raf.mod.uk/universityairsquadrons/findasquadron/ouas.cfm}
\descript{| Officer Cadet}
\location{Oct 2013 – June 2014 | Oxford University Air Squadron, Oxford, UK}
\begin{tightemize}
\item Tutored to fly the Grob G 115 totalling 4hrs flight time. 
\item Challenged continually with intense solo and team based activities. 
\item Light physical and weapons training.
\end{tightemize}
\sectionsep

\experience{5PORE}{http://theowindebank.co.uk}
\descript{| Web Developer / Graphic Designer / Artist}
\location{Sept 2010 – March 2015}
\begin{tightemize}
\item Designed, developed and maintained a website showing and selling personal work.
\item Ranges from skateboards to fully featured websites. 
\item Involved regular interaction with clients located worldwide.
\end{tightemize}
\sectionsep

\experience{The Golden Lion}{}
\descript{| Bar Staff}
\location{July 2014 – Oct 2014 | Corbridge, UK}
\begin{tightemize}
\item Served food and drink, often in high pressure circumstances. 
\item Responsibilities included general bar maintenance and managing guest accommodation.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming/Software}
\skill{Advanced:} Matlab \textbullet{} PHP \textbullet{} jQuery \textbullet{} \LaTeX\ \textbullet{} MySQLi \textbullet{} Shell \textbullet{} HTML \textbullet{} CSS  \\ Office Suite \textbullet{} Photoshop\\
\skill{Intermediate:} Git \textbullet{} JavaScript\\
\skill{Basic:} Python \textbullet{} Java \textbullet{} C
\sectionsep
\vspace{1cm}

\end{minipage} 
\address{{\fontspec{Helvetica Neue Thin}home address:} Calder Cottage, St. Helen's Lane, Corbridge, Northumberland, NE455JD\\
\vfill
\noindent {\fontspec{Helvetica Neue Thin}term address:} St. Catherine's College, Manor Rd., Oxford, OX13UJ}

\end{document}  
