\cvsection{Experience}
\begin{cventries}
    \cventry
    {Software Engineer}
    {Cue Sense Ltd.}
    {London, UK}
    {Jun. 2017 – Current}
    {
      \begin{cvitems}
        \item {Lead the design of a comprehensive code-base for a product designed to help visually impaired people to interpret non-verbal cues, utilising computer vision and machine learning.}
        \item {Constructed the entire image processing, image classification, and binaural sound feedback pipeline for the software prototype, using Python 3.6 and a multitude of advanced data science techniques. This has built upon my experience of creating unique machine learning pipelines for novel applications.}
        \item{Followed strict OOP conventions and placed high emphasis on code design, refining my abilities in writing modular, expandable, and unit-tested packages to a professional level.}
        \item {Designed around challenging physical and economical constraints, helping expand my knowledge and practical experience in designing software architecture and core algorithms for market-facing products.}
        \item {Pitched the product to potential investors, heightening my awareness and understanding of the marketing and business aspects to developing a novel, innovative product.}
      \end{cvitems}
    }
    \cventry
    {Software Developer Intern}
    {Machine Learning Research Group}
    {University of Oxford}
    {Jul. 2016 – Sep. 2016}
    {
      \begin{cvitems}
        \item {Used a variety of machine learning techniques during my internship within the Oxford-Man Institute of Quantitative Finance, working on a project to detect mosquito presence, species, and gender from audio recordings.}
        \item {Developed a fully-featured python package to act as a test-bed for detection algorithms, aimed for a public open source release. This has improved my skills in coding for a long-term project where the code will be further used and worked on by others.}
        \item {Planned and carried out a series of microphone tests, resulting in a large batch of microphones being purchased and used to capture further biological recordings.}
        \item {Built upon this work within my fourth year university project, recieving a mark of 83 on final grading.}
        \item{Feedback from supervisors placed me in the top 5\% of students who have worked with the Oxford-Man institute, confirming my ability to carry out high value work in this sector.}
      \end{cvitems}
    }
    \cventry
    {Software Developer}
    {Engineers Without Borders}
    {Oxford, UK}
    {Nov. 2015 – Mar. 2016}
    {
      \begin{cvitems}
        \item {Built a data collection system for a team to gather and process information on malaria cases in rural Peru with a PHP/MySQL back-end, improving my project management and team-work skills.}
      \end{cvitems}
    }
  \cventry
    {Research Assistant}
    {Communications, Sensors, Signal and Information Processing Research Group}
    {Newcastle University, UK}
    {Jul. 2015 – Sep. 2015}
    {
      \begin{cvitems}
        \item {Internship working on various sonar systems to image undersea objects beneath the seabed.}
        \item {Implemented a variety of processing techniques in MATLAB including delay-sum beam-forming, synthetic
aperture focusing and signal filtering. Challenging problems encountered during the project enhanced my problem solving and research skills.}
      \end{cvitems}
    }
%   \cventry
%     {Modelling and Analysis Technician}
%     {Skalene Ltd.}
%     {Cambridge, UK}
%     {Jul. 2014 - Apr. 2015}
%     {
%       \begin{cvitems}
%         \item {Simulated heat flow between parts of a novel PCR design used to amplify DNA, improving my modelling skills.}
%       \end{cvitems}
%     }
%   \cventry
%     {Officer Cadet}
%     {Oxford University Air Squadron}
%     {Oxford, UK}
%     {Oct. 2013 - Jun. 2014}
%     {
%       \begin{cvitems}
%         \item {Tutored to fly the Grob G 115 totalling 4hrs flight time, increasing my ability to make quick decisions in high-pressure environments.}
%         \item {Challenged continually with intense individual and team-based activities, advancing team planning skills.}
%       \end{cvitems} 
%     }
  \cventry
    {Web Developer / Graphic Designer / Artist}
    {5PORE}
    {}
    {Sep. 2010 - Mar. 2015}
    {
      \begin{cvitems}
        \item {Designed, developed and maintained a website showing and selling personal work to clients worldwide, giving me strong inter-personal communication skills and experience running a self-directed project.}
      \end{cvitems}
    }
\end{cventries}
